\documentclass{letter}
\usepackage{hyperref}
\addtolength{\topmargin}{-1.5in}
\addtolength{\textheight}{2.0in}


\signature{Ahmed \& Emily}
\address{\input{address.tex}}
\begin{document}


\begin{letter}{
  The Honorable Robert Portman \\
  37 West Broad Street \\
  Room 300 \\
  Columbus, OH 43215}

\opening{Dear Senator Portman,}

We wrote to you yesterday asking you to speak out about the current administration's repudiation of science, its personal attacks on journalists, its gutting of the EPA and USDA putting citizens' health at risk, and its xenophobic immigration executive order.

We were incredibly relieved, and very grateful, to see you acknowledge that the executive order was deeply flawed. As you said, America {\em is} a beacon to the rest of the world---it certainly was to Ahmed's parents, who are Muslims that emigrated from India twenty-five years ago and have given everything they had to this country.

Despite crime and terrorism in America being at near-all-time lows, we agree with you that more could be done to make us safer. America’s prison system are designed to ensure re-enrollment, not rehabilitation. Our society widely ignores mental healthcare. It treats drug addiction as a crime instead of a disease. We are proud to see you take an active role in {\em constructively} addressing opoid addiction. It's steps like {\em this} that will increase our security, at home and in the world. Not by ignorant and ill-conceived executive orders.

We thank you for your continuing work to check this administration's excesses.

\closing{Very respectfully,}


\end{letter}
\end{document}
