\documentclass{letter}
\usepackage{hyperref}
\usepackage{csquotes}
\addtolength{\topmargin}{-1.5in}
\addtolength{\textheight}{2.0in}


\signature{Ahmed \& Emily}
\address{\input{address.tex}}
\begin{document}


\begin{letter}{
  The Honorable Michael Turner \\
  120 West 3rd St, Ste. 305 \\
  Dayton, OH 45402}

\opening{Dear Mr Turner,}

We wrote to you yesterday asking you to speak out about the current administration's repudiation of science, its personal attacks on journalists, its gutting of the EPA and USDA putting citizens' health at risk, and its xenophobic immigration executive order. We are writing to you again today about this last issue.

At a time when so many of your colleagues in the House of Representatives, as well as Senators Portman and Brown, and Governor Kasich all have condemned the immigration executive order as ill-conceived, counter-productive, and heartless, your silence on this is tremendously disappointing.

Eliot Cohen, who advised Condoleezza Rice when she was Secretary of State under President Bush, writes in last Sunday's {\it The Atlantic},

\begin{displayquote}
For the community of conservative thinkers and experts, and more importantly, {\bf conservative politicians}, this is a testing time. Either you stand up for your principles and for what you know is decent behavior, or you go down, if not now, then years from now, as a coward or opportunist. Your reputation will never recover, nor should it. (Emphasis mine.)
\end{displayquote}

We are eagerly awaiting your response.

\closing{Very respectfully,}


\end{letter}
\end{document}
