\documentclass{letter}
\usepackage{hyperref}
\addtolength{\topmargin}{-1.5in}
\addtolength{\textheight}{2.0in}


\signature{Ahmed \& Emily}
\address{\input{address.tex}}
\begin{document}


\begin{letter}{
  The Honorable Michael Turner \\
  120 West 3rd St, Ste. 305 \\
  Dayton, OH 45402}

\opening{Dear Mr Turner,}

Thank you for your letted dated November 21, 2016, promising to follow the progress of H.R.20 and campaign finance reform and public-funding of elections. We continue to believe that limiting the corrupting influence of money in politics should be the number one ``meta-goal'' of Congress, a goal that was loudly called for during last year's campaign, including by now-President Trump but seems to have been largely forgotten.

But today we are writing to you about the behavior of President Trump this past week. We want you to know that his behavior during his first week is has left us appalled, flabbergasted, and outraged.

We find it appalling that the administration has sought to discredit and suppress science, so much of which was done at our alma mater of Ohio State and by fine universities in your district, including Wright State.

We find it frightening that the administration is elevating the profits of businesses above the health and welfare of citizens by mistreating the EPA and USDA.

We find it heart-breaking that the administration is peddling xenophobia as a means of crime prevention.

We find it inconceivable that the administration has called for individual journalists critical of these outrages to be fired.

And we are surprised to see no word from your office denouncing this behavior. Please let us know what you are planning to do about this suppression of science, this threat to the environment, this oppression of guests of our country, and this slandering of our media, by the highest office of the land.



\closing{Very respectfully,}


\end{letter}
\end{document}
